The problem and promise of scale in multilayer animal social networks

### 2020-02-12 paper/manuscript.Rmd
appropriate

In general, individuals in multilayer networks became more connected as social
scale increased; however, this relationship varied by habitat type and season.
As social scale increased, graph strength for winter networks increased to
~100-200 m thresholds, followed by a plateau, while graph strength for summer
networks did not change as the social threshold increased (Figure
\@ref(fig:socres)a). Layer relevance increased for winter networks between 5 and
50 m social thresholds, then did not change for any habitat types which suggests
the winter habitat layers captured most, if not all, of the potential
connections an individual would have across these networks (Figure
\@ref(fig:socres)b). Connective redundancy increased rapidly when groups were
formed up to ~100 m threshold, followed by a plateau and slight decrease at
higher thresholds, presumably due to an increase in summer forest degree at ~500
m (Figure \@ref(fig:socres)d). Taken together, these results suggest the optimal
social scale at which groups should be assigned is likely somewhere between
~20-100 m based on the rate at which network metrics stabilized. For ungulates,
groups are often assigned based on 50 m threshold (Lingle 2003; Lesmeries et al.
2018; Peignier et al. 2019), suggesting that given similar quantities of data,
~50 m is likely an ideal social scale for generating social networks in caribou
and similar species.
<!-- TODO: missing summer relevance and all layer similarily-->

>>>>

In general, individuals in multilayer networks became more connected as social
scale increased; however, this relationship varied by habitat type and season.
As social scale increased, graph strength for winter networks increased to
~100-200 m thresholds, followed by a plateau, while graph strength for summer
networks did not change as the social threshold increased (Figure
\@ref(fig:socres)a). Layer relevance increased for winter networks between 5 and
50 m social thresholds, then did not change for any habitat types which suggests
the winter habitat layers captured most, if not all, of the potential
connections an individual would have across these networks (Figure
\@ref(fig:socres)b). Connective redundancy increased rapidly when groups were
formed up to ~100 m threshold, followed by a plateau and slight decrease at
higher thresholds, presumably due to an increase in summer forest degree at ~500
m (Figure \@ref(fig:socres)d). Taken together, these results suggest the optimal
social scale at which groups should be assigned is likely somewhere between
~20 - 100 m based on the rate at which network metrics stabilized. For ungulates,
groups are often assigned based on 50 m threshold (Lingle 2003; Lesmeries et al.
2018; Peignier et al. 2019), suggesting that given similar quantities of data,
~50 m is likely an appropriate social scale for generating social networks in caribou
and similar species.
<!-- TODO: missing summer relevance and all layer similarily-->
